\documentclass[12pt]{paper}
\usepackage[english]{babel}
\usepackage{indentfirst}
\usepackage{graphicx}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb,amsfonts}
\usepackage{multicol}
\usepackage{xcolor}
\usepackage{changepage}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{textcomp}
\usepackage{mathtools}
\usepackage{comment}
\usepackage[normalem]{ulem}
\usepackage{marginnote}
\usepackage[numbers,sort&compress]{natbib}
\mathtoolsset{showonlyrefs=false}

\newcommand{\ga}{\alpha}
\newcommand{\gb}{\beta}
\newcommand{\gam}{\gamma}
\newcommand{\gd}{\delta}
\newcommand{\eps}{\epsilon}
\newcommand{\veps}{\varepsilon}
\newcommand{\gz}{\zeta}
\newcommand{\gt}{\theta}
\newcommand{\gi}{\iota}
\newcommand{\gk}{\kappa}
\newcommand{\gl}{\lambda}
\newcommand{\gs}{\sigma}
\newcommand{\go}{\omega}
\newcommand{\Gam}{\Gamma}
\newcommand{\gD}{\Delta}
\newcommand{\gT}{\Theta}
\newcommand{\gL}{\Lambda}
\newcommand{\gS}{\Sigma}
\newcommand{\gO}{\Omega}

%%%%%%%%%

\newcommand{\pt}[1]{\left( #1\right)}
\newcommand{\pq}[1]{\left[ #1 \right]}
\newcommand{\pg}[1]{\left\{ #1\right\}}
\newcommand{\figref}[1]{\figurename~\ref{#1}}
\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\gray}[1]{\textcolor{gray}{#1}}
\newcommand{\wikilink}[2] { \href{#1.pdf}{#2}\,(\href{#1.tex}{edit})}

\setlength{\textheight}{20cm}
\changepage{2.5cm}{3.0cm}{-4cm}{-1.0cm}{-2cm}{-2cm}{-0.6cm}{0.5cm}{0cm}
\pagestyle{fancy}
\lhead{\bf \today}
\chead{\bf }
\rhead{EG}
\title{O\today}
\author{EG}
\date{\today}

\begin{document}
 \maketitle
\wikilink{home}{Home}

\wikilink{ideas}{Ideas}
 
\wikilink{metabolism}{Self}

\section{Citric and reverse citric acid cycles as origin of life}
Discussion is in the following papers:
\begin{itemize}
 \item 
 Morowitz, H.J.; Kostelnik, J.D.; Yang, J.; Cody, G.D. The origin of intermediary metabolism. Proc.
Natl. Acad. Sci. USA 2000, 97, 7704–7708.
\item 
 Smith, E.; Morowitz, H.J. Universality in intermediary metabolism. Proc. Natl. Acad. Sci. USA
2004, 101, 13168–13173.
\item 
 Wächterhäuser, G. Evolution of the first metabolic cycles. Proc. Natl. Acad. Sci. USA 1990,
87, 200–204.
\item 
 Wächterhäuser, G. On the chemistry and evolution of the pioneer organism. Chem. Biodivers.
2007, 4, 584–602.
\item 
 Ross, D.S. The viability of a nonenzymatic reductive citric acid cycle—Kinetics and
thermochemistry. Origins Life Evol. Biosphere 2007, 37, 61–65.
\item 
 Orgel, L.E. The implausibility of metabolic cycles on the prebiotic earth. PLoS Biology 2008, 6,
5–13.
\item 
 Kalapos, M.P. The energetics of the reductive citric acid cycle in the pyrite-pulled surface
metabolism in the early stage of evolution. J. Theor. Biol. 2007, 248, 251–258.
\item 
 Powner, M.W.; Gerland, B.; Sutherland, J.D. Synthesis of activated pyrimidine ribonucleotides in
prebiotically plausible conditions. Nature 2009, 459, 239–242.

\end{itemize}

 
\end{document}
